---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CSIAIndxs

<!-- badges: start -->
<!-- badges: end -->

The goal of CSIAIndxs is to ...

## Installation

You can install the released version of CSIAIndxs from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("CSIAIndxs")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r label_TS_Nitrogen}
library(CSIAIndxs)
data("DATASET")

df <- label_TS_Nitrogen(df = DATASET)
```


```{r}
df <- calc_TP(df = df)
```




```{r calc_sum_v}

df <- calc_sum_v(df = df)
```

```{r}

df <- pull_AA(df = df, AA_nm = "Phe")

library(ggplot2)
ggplot() +
  geom_point(data = df, aes(x = smp, y = Phe, color = smp), size = 4) +
  theme_bw()

```


```{r}
df <- calc_source_mean(id_col = "smp", 
                       corrected_data_col = "Corrected_delta_15_N" ,
                       std_col = "Stdev",
                       data = df)


df

```





You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
